---
title: "Malicious domain names detection with H2O"
author: "JG Pardyak"
date: "31-3-2022"
output: 
  ioslides_presentation:
    widescreen: true
    logo: logo.svg
    css: ../WWW/styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, results='asis'}
cat("## . ")
#cat('<h2 class="red-text" style="color: #1c3f6e;">&nbsp;First slide</h2>')
```

<h2 class="red-text" style="color: #1c3f6e;">&nbsp;First slide</h2>

```{r, results='asis'}
cat("## . ")
#cat('<h2 class="red-text" style="color: #1c3f6e;">&nbsp;First slide</h2>')
```

<h2 class="red-text" style="color: #1c3f6e;">&nbsp;Second slide</h2>

## . Markdown 1

This • is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.


## •Markdown 2


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## .Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## .Share your feedback

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Dinner

ss


## Next Steps 


