---
title: "Malicious domain names detection with H2O"
author: "JG Pardyak"
#date: "31-3-2022"
#output: 
#  slidy_presentation:
#    css: WWW/styles.css
    
output:
  xaringan::moon_reader:
#    css: ["default", "WWW/blackboard-white.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# R Markdown 1

## R Markdown 2

### R Markdown 3 {#teamdotblue .emphasized}

---

## R Markdown

--- 

background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
background-size: 100px
background-position: 90% 8%

--- 

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

---

# remark.js

---

## Next Steps {#nextsteps .emphasized}


## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

